% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Xiaowu (Horace) He}

\basicInfo{
  \email{horacehxw@gmail.com} \textperiodcentered\ 
  \phone{(510)944-6937} \textperiodcentered\ 
  \linkedin{https://www.linkedin.com/in/horacehxw}}
  
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of California, Berkeley}, California, America}{2017 -- Present}
\textit{Exchange Study} in Computer Science and Electronic Engineering, Spring 2017
\begin{itemize}
%  \item GPA: ----
  \item Relative Course: Data Structure (CS 61B), Computer Architechture (CS 61C), Probability and Random Process (EE 126), Innovation and Entrepreneurship (UGBA 196)
\end{itemize}

\datedsubsection{\textbf{University of Electronic Science and Technology of China}, Sichuan, China}{2015 -- Present}
\textit{Study} in Yingcai Honors College, \textit{Major} at Computer Science

\section{\faUsers\ Projects}
\datedsubsection{\textbf{Two Stage Pipelined CPU}}{Mar. 2017 -- Present}
Using Logisim to implement a simple 16-bit two-cycle processor, with an ISA that uses a subset of MIPS instructions on a slightly different archticture.

\datedsubsection{\textbf{Relational Database Management System} }{Feb. 2017 -- Mar. 2017}
%\role{Java}{Course Project in CS 61B}
Created a program that accepts a limited range of commands, similar to the Redis Database. Accepts input from stdin or a file.
\begin{itemize}
  \item Implemented by Java.
  \item Accept table join, condition and arithmetic operation.
%  \item See spec: http://datastructur.es/sp17/materials/proj/proj2/proj2.html#overview.
\end{itemize}

\datedsubsection{\textbf{Digital Communication System}}{Mar. 2017 -- Mar. 2017}
%\role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
Build a system from scratch to transmit a text file between two laptops, using only the speakers and microphones of the computers.
\begin{itemize}
  \item Implemented in Python, using numpy, reedsolo and pyaudio library.
  \item Bit-rate of at least 100 bits per second.
  \item Apply RS-code as error correction.
\end{itemize}

\datedsubsection{\textbf{MIPS assembler and linker}}{Mar. 2017 -- Mar. 2017}
Translates a subset of the MIPS instruction set to machine code. The assembler is a two-pass assembler to resolve forwarding problem.
\begin{itemize}
  \item Implemented in C and MIPS assembly.
  \item Use two-pass assemble process to avoid forwarding problem.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Proficiency: C, Java
  \item Intermediate: Python, MIPS, Git
  \item Basic: C++, Matlab, Microsoft Office Suite
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
\datedline{Other awards}{2015}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
%  \item Blog: http://your.blog.me
  \item GitHub: https://github.com/Horacehxw
  \item Languages: English - Working Proficiency, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
